Automatically Splitting a Staged Lambda Calculus

### 2015-07-09 paper/relatedwork.tex
in the middle of fixing related work

Algorithms similar to ours have appeared in the partial evaluation community,
where they are used as a preprocessing step to partial evaluation. 
For instance, \cite{Mogensen89a} and \cite{DeNiel91} defined splitting algorithms
for programs consistening of a set of first-order recursive functions.
In addition to the lack of first-class functions, 
the binding time specificiations used by these systems are more complicated and less expressive than the type system of \lang.
The question of binding time analysis for a higher-order language was visited in \cite{Mogensen89b},
however the implications for splitting were not explicitly considered.

>>>>

Algorithms for stage splitting have appeared in the literature under the names 
{\em pass separation}, {\em binding time separation}, {\em data specialization}, 
{\em program bifurcation}, and as various unnamed compiler passes.

In the partial evaluation community, stage splitting has been investigated 
mostly as a preprocessing step for self-applied partial evaluators. 
For instance, \cite{Mogensen89a} and \cite{DeNiel91} defined splitting algorithms
for programs consistening of a set of first-order recursive functions.
Those works used a grammar-based binding-time specification that's 
relatively complicated compared to the type system of \lang.
This complication mostly stems from the decision to start with an untyped language;
.

In addition to the lack of first-class functions, 
the binding time specificiations used by these systems are more complicated and less expressive than the type system of \lang.

The question of binding time analysis for a higher-order language was visited in \cite{Mogensen89b},
however the implications for splitting were not explicitly considered.
